\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Wayne Havey Journal \#8\\
}

\author{\IEEEauthorblockN{ Wayne R. Havey III}
\IEEEauthorblockA{\textit{PhD Student: Security Track} \\
\textit{UCCS}\\
Colorado Springs, CO \\
whavey@uccs.edu}
}

\maketitle

\section{Review and Survey Paper Learning}
\subsection{Reviewing}
For reviewing, I had one paper that was very far from finished and one that was very long. 
For the paper that was not complete I tried to give as much feedback as possible using my best judgment for where the paper was headed.
For the longer paper it was longer because there wasnt a great breakup of sections and subsections and there were few diagrams or other things that broke up the text enough for it not feel too dense. 
Both papers seemed to lack the structure expected for a survey paper. 
They felt more like research papers.
I also received somewhat similar feedback so I think I understand more now what a survey paper should look like and I should be able to restructure my paper to reflect that. 

\subsection{Writing}
I learned a lot of standard formatting for latex from my advisor.
I had forgotten what we discussed in class about making each section its own document and my advisor reminded me of that.
She explained how that would be helpful for reviewing, editing, and doing git 'diffs'. 
She also explained that it is a good practice to make every sentence of a paragraph its own line in latex.
I had being writing paragraphs normally.
She explained it is more like code and each sentence is like a line of code. 
Additionally, I had been using \textbackslash\textbackslash to separate each paragraph and now I know its better to just use and empty line.

As I mentioned earlier I think I have a better idea now on how to structure the survey paper. 
I need to spend some time interspersing my examples of the classification into the paper naturally instead of breaking it out into one long list.
\end{document}
